---
title: "ggCyberPunk"
author: "Joshua de la Bruere"
date: "4/2/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))

```

```{r echo = F, message=F, warning=F}
library(tidyverse)
library(ggCyberPunk)

df = data.frame(A=c(1,4,4,6,7,5,1),
               B=c(4,3,5,7,5,6,7),
               Time=c(1,2,3,4,5,6,7)) %>%
pivot_longer(cols = c(A,B),names_to = "group", values_to = "count")


df %>%
   ggplot(aes(x=Time, y = count, color = group, fill= group))+
     geom_glowing_area()+
    theme_cyberpunk()+
     scale_fill_cyberpunk("cotton candy")+
     scale_color_cyberpunk("cotton candy")+
  ggtitle("Introducing Cyberpunk plots", subtitle = "Using ggCyberPunk")

```


## Installation
This isn't on CRAN, so you'll have to use devtools. 

``devtools::install_github("delabj/ggCyberPunk")``

## Why?
The other day, I saw a post on [reddit](https://www.reddit.com/r/rstats/comments/fsncqz/cyberpunk_plots_in_r/) asking if there was a way to create a "CyberPunk plot" in R. This was based on plots produced in python using matplotlib as shown on [this repo](https://github.com/dhaitz/mplcyberpunk). Since it's the end times, and I have nothing better to do at home than poke around with a theme, this seemed like a perfect fit.

If you want more cyberpunk themed plot options, palettes, and themes, check out [vapoRwave](https://github.com/moldach/vapoRwave), from which I totally stole the base theme for this package. A few modifications, but it's very much the new_retro theme.


## What's in the box?


### geom_glowing_area()

A glowing area plot for a cyberpunk/disco/neon vibe.

#### Useage 
geom_glowing_area(alpha =  1, size = 1, glow_alpha = 0.03)

#### Arguments

`alpha`: the alpha level of the base line
`size`: size of the base line
`glow_alpha`: set the alpha level of the glow layers

#### Example
```{r, message=F, warning=F}
library(tidyverse)
library(ggCyberPunk)

df = data.frame(A=c(1,4,4,6,7,5,1),
               B=c(4,3,5,7,5,6,7),
               Time=c(1,2,3,4,5,6,7)) %>%
pivot_longer(cols = c(A,B),names_to = "group", values_to = "count")


df %>%
   ggplot(aes(x=Time, y = count, color = group, fill= group))+
     geom_glowing_area()+
     theme_cyberpunk()+
     scale_fill_cyberpunk("zune")+
     scale_color_cyberpunk("zune")+
  ggtitle("geom_glowing_area()", subtitle = "From ggCyberPunk")

```


### geom_glowing_line()

A glowing line plot for a cyberpunk/disco/neon vibe.

#### Useage 
geom_glowing_line(alpha =  1, size = 1, glow_alpha = 0.03)

#### Arguments

`alpha`: the alpha level of the base line
`size`: size of the base line
`glow_alpha`: set the alpha level of the glow layers

#### Example
```{r, message=F, warning=F}
library(tidyverse)
library(ggCyberPunk)

df = data.frame(A=c(1,4,4,6,7,5,1),
               B=c(4,3,5,7,5,6,7),
               Time=c(1,2,3,4,5,6,7)) %>%
pivot_longer(cols = c(A,B),names_to = "group", values_to = "count")


df %>%
   ggplot(aes(x=Time, y = count, color = group, fill= group))+
     geom_glowing_line()+
     theme_cyberpunk()+
     scale_color_cyberpunk()+
  ggtitle("geom_glowing_line()", subtitle = "From ggCyberPunk")

```

### geom_linesaber()

A glowing line plot for a laser sword look.

#### Useage 
geom_linesaber(alpha =  1, size = 1, glow_alpha = 0.03)

#### Arguments

`alpha`: the alpha level of the base line
`size`: size of the base line
`glow_alpha`: set the alpha level of the glow layers

#### Example
```{r, message=F, warning=F}
library(tidyverse)
library(ggCyberPunk)

df = data.frame(A=c(1,4,4,6,7,5,1),
               B=c(4,3,5,7,5,6,7),
               Time=c(1,2,3,4,5,6,7)) %>%
pivot_longer(cols = c(A,B),names_to = "group", values_to = "count")


df %>%
   ggplot(aes(x=Time, y = count, color = group, fill= group))+
     geom_linesaber()+
     theme_cyberpunk()+
     scale_color_linesaber(reverse = T)+
  ggtitle("geom_linesaber()", subtitle = "From ggCyberPunk")

```


## Also included are palettes

### main
```{r,echo=F, warning=F, message=F}
scales::show_col(c('cyber1 blue' = "#08F7FE",
  'cyber2 pink' = "#E64E8D",
  'cyber3 yellow' = "#ECCE8E",
  'cyber4 orange' = "#EE9537"))
```
### Cotton Candy
```{r,echo=F, warning=F, message=F}
scales::show_col(c('cyber1 blue' = "#08F7FE",
  'cyber2 pink' = "#E64E8D"))
```
### zune
```{r,echo=F, warning=F, message=F}
scales::show_col(c(
  'cyber2 pink' = "#E64E8D",
  'cyber4 orange' = "#EE9537"))
```
### main
```{r,echo=F, warning=F, message=F}
scales::show_col(c(  'saber2 green' = "#32CD32",
  'saber3 red' = "#B22222",
  'saber4 purple' = "#8510d8",
  'saber1 blue' = "#49f9fe"))
```


## scale_fill_cyberpunk/scale_color_cyberpunk

### usage
`scale_fill_cyber_punk(palette = "main", discrete = T, reverse = F )`
`scale_color_cyber_punk(palette = "main", discrete = T, reverse = F )`


## scale_fill_linesaber/scale_color_linesaber

### usage
`scale_fill_linesaber(palette = "main", discrete = T, reverse = F )`
`scale_color_linesaber(palette = "main", discrete = T, reverse = F )`

